---
title: "Step 4 for zscorePG"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
RAWmisc::InitialiseProject(
  HOME = "/git/code_minor/hanna_paper_3/",
  RAW = "/analyses/data_raw/hanna_paper_3/",
  CLEAN = "/analyses/data_clean/hanna_paper_3",
  BAKED = "/analyses/results_baked/hanna_paper_3/",
  FINAL = "/analyses/results_final/hanna_paper_3/",
  SHARED = "/dropbox/clients/hanna/paper_3/richard/")

library(data.table)
library(ggplot2)

if(!exists("d")) d <- haven::read_spss(file.path(RAWmisc::PROJ$RAW,"alla_large_final.sav"))
index <- d$im_participating_preg==1
index[is.na(index)] <- FALSE
d <- d[index,]
```

## Investigate dataset

After including the `im_participating_preg` variable we have `r nrow(d)` participants.

```{r}
table(d$v32_SSRI, useNA="always")
```

```{r}
table(d$v32_EPDS_D2_9R, useNA="always")
```

\newpage

## Full model
```{r}
fitFull <- lm(zscorePG ~
  v32_EPDS_D2_9R +
  v32_SSRI +
  im_fasting_sample +
  SIN_366_preg +
  COS_366_preg +
  SIN_183_preg +
  COS_183_preg,
  data = d
  )
fitNoSeasonality <- lm(zscorePG ~
  v32_EPDS_D2_9R +
  v32_SSRI +
  im_fasting_sample,
  data = fitFull$model
  )
summary(fitFull)
```

This full model has `r nrow(fitFull$model)` observations in it. Shouldn't we only have 281?

\newpage

## Testing for overall seasonality
We now test for all seasonality at once:
```{r}
anova(fitNoSeasonality,fitFull)
```

It appears that there is significant seasonality in this data

\newpage

## Testing individual seasonality components
We now fit the two lesser models that we use to perform the F test on:
```{r}
fitNo366 <- lm(zscorePG ~ 
  v32_EPDS_D2_9R +
  v32_SSRI +
  im_fasting_sample +
  SIN_183_preg +
  COS_183_preg,
  data = d
  )

fitNo183 <- lm(zscorePG ~ 
  v32_EPDS_D2_9R +
  v32_SSRI +
  im_fasting_sample +
  SIN_366_preg +
  COS_366_preg,
  data = d
  )
```

Testing the significance of the 366 day period cosine functions (they are significant):
```{r}
anova(fitNo366,fitFull)
```


Testing the significance of the 183 day period cosine functions (they are significant):
```{r}
anova(fitNo183,fitFull)
```

\newpage

## Graphical interpretation

```{r, fig.height=4}
estimates <- coef(fitFull)
sin366 <- estimates[names(estimates)=="SIN_366_preg"]
cos366 <- estimates[names(estimates)=="COS_366_preg"]

sin183 <- estimates[names(estimates)=="SIN_183_preg"]
cos183 <- estimates[names(estimates)=="COS_183_preg"]

estimates366 <- sin366*sin(c(1:366)/366*2*pi) + cos366*cos(c(1:366)/366*2*pi)
estimates183 <- sin183*sin(c(1:366)/183*2*pi) + cos183*cos(c(1:366)/183*2*pi)

plot <- data.table(estimates366,estimates183,day=c(1:366))
plot[,estimatesBoth:=estimates366+estimates183]
plot <- melt.data.table(plot,id="day")
switch <- c("estimatesBoth"="Combined",
            "estimates183"="183 day period",
            "estimates366"="366 day period")
RAWmisc::RecodeDT(plot,switch,"variable")
plot[,variable:=factor(variable,levels=switch)]

q <- ggplot(plot, aes(x=day,y=value,colour=variable))
q <- q + geom_line()
q <- q + scale_x_continuous("Day")
q <- q + scale_y_continuous("Effect on IF Marker")
q <- q + scale_color_brewer("",palette="Set1")
q
```


## Interpretation of 366 day period cosine functions

Let us focus on your regression estimates for the 366 day period cosine functions, where we will call $b_1$ and $b_2$ the coefficients for SIN366 and COS366 respectively.

```{r}
estimates <- coef(fitFull)
b1 <- estimates[names(estimates)=="SIN_366_preg"]
b2 <- estimates[names(estimates)=="COS_366_preg"]

t <- atan(b1/b2)*366/2/pi
```

$$
\begin{aligned}
\begin{split}
               T ={}& \text{Period} \\
                 ={}& \text{366 days} \\
\text{Amplitude} ={}& \sqrt{b_1^2+b_2^2} \\
                 ={}& \sqrt{ `r formatC(b1,digits=2,format="f")`^2 + `r formatC(b2,digits=2,format="f")`^2 }\\
                 ={}& `r formatC(sqrt(b1^2+b2^2),digits=2,format="f")` \\
               t ={}& \text{Precursor to location of peaks/troughs} \\
                 ={}& \text{arctan}(b_1 / b_2) \times T / 2 / \pi \\
                 ={}& \text{arctan}( `r formatC(b1,digits=2,format="f")` / `r formatC(b2,digits=2,format="f")`) \times 366 / 2 / \pi \\
                 ={}& `r formatC(t, digits=0, format="f")`
\end{split}\\
\end{aligned}
$$

If $b_1$/ $b_2$ = `r formatC(b1,digits=2,format="f")` / `r formatC(b2,digits=2,format="f")` = `r formatC(b1/b2,digits=2,format="f")` > 0, then t > 0 and indicates the first extreme; the other extreme value is found at t + T/2. If  $b_1$/ $b_2$ < 0, then t < 0; the extreme values are found at t + T/2 and at t+T. If $b_1$ > 0,the first extreme is a maximum and the second a minimum;

t = `r formatC(t, digits=0, format="f")` > 0, which means the maximum (peak) is at `r formatC(t, digits=0, format="f")` days and the minimum (trough) is at `r formatC(t+366/2, digits=0, format="f")` days.

\newpage

## Interpretation of 183 day period cosine functions

Let us focus on your regression estimates for the 183 day period cosine functions, where we will call $b_1$ and $b_2$ the coefficients for SIN183 and COS183 respectively.

```{r}
estimates <- coef(fitFull)
b1 <- estimates[names(estimates)=="SIN_183_preg"]
b2 <- estimates[names(estimates)=="COS_183_preg"]

t <- atan(b1/b2)*183/2/pi
```

$$
\begin{aligned}
\begin{split}
               T ={}& \text{Period} \\
                 ={}& \text{183 days} \\
\text{Amplitude} ={}& \sqrt{b_1^2+b_2^2} \\
                 ={}& \sqrt{ `r formatC(b1,digits=2,format="f")`^2 + `r formatC(b2,digits=2,format="f")`^2 }\\
                 ={}& `r formatC(sqrt(b1^2+b2^2),digits=2,format="f")` \\
               t ={}& \text{Precursor to location of peaks/troughs} \\
                 ={}& \text{arctan}(b_1 / b_2) \times T / 2 / \pi \\
                 ={}& \text{arctan}( `r formatC(b1,digits=2,format="f")` / `r formatC(b2,digits=2,format="f")`) \times 183 / 2 / \pi \\
                 ={}& `r formatC(t, digits=0, format="f")`
\end{split}\\
\end{aligned}
$$

If $b_1$/ $b_2$ = `r formatC(b1,digits=2,format="f")` / `r formatC(b2,digits=2,format="f")` = `r formatC(b1/b2,digits=2,format="f")` > 0, then t > 0 and indicates the first extreme; the other extreme value is found at t + T/2. If  $b_1$/ $b_2$ < 0, then t < 0; the extreme values are found at t + T/2 and at t+T. If $b_1$ > 0,the first extreme is a maximum and the second a minimum;

t = `r formatC(t, digits=0, format="f")` > 0, which means the maximum (peak) is at `r formatC(t, digits=0, format="f")` and `r formatC(t+183, digits=0, format="f")` days and the minimum (trough) is at `r formatC(t+183/2, digits=0, format="f")` and `r formatC(t+183/2+183, digits=0, format="f")` days.



