---
title: "Safer Births DMC"
author: "Richard White"
date: "`r lubridate::today()`"
output:
  pdf_document: default
---
```{r setup, message=FALSE, warning=FALSE, include=FALSE}
RAWmisc::InitialiseProject(
  PROJHOME = "/analyses/code_minor/safer_births/",
  PROJRAW = "/analyses/data_raw/safer_births/",
  PROJCLEAN = "/analyses/data_clean/safer_births",
  PROJBAKED = "/analyses/results_baked/safer_births/",
  PROJFINAL = "/analyses/results_final/safer_births/",
  PROJSHARED = "/dropbox/results_shared/safer_births/")

library(data.table)
data <- haven::read_spss(file.path(RPROJ$PROJRAW,"MNH RCT 08JAN17-2.sav"))
data <- data.table(data)
```

# SIGNIFICANCE DECISIONS
We consider an alpha cut-off of 0.05 to be statistically sigificant

# RESULTS
- Not statistically significant difference in the secondary outcome low apgar score (<7) at 5th minute due to device assignment (p-value 0.943)
- Not statistically significant difference in the secondary outcome stillbirths at 30 minutes due to device assignment (p-value 0.641)
- Not statistically significant difference in the secondary outcome death at 24 hours due to device assignment (p-value 0.996)
- Not statistically significant difference in the secondary outcome in treatment at 24 hours due to device assignment (p-value 0.127)
- Not statistically significant difference in the secondary outcome death at 24 hours and/or in treatment at 24 minutes due to device assignment (p-value 0.115)

# CONCLUSION
- Do not terminate study early

\newpage
# CLEANING
## Secondary outcomes
```{r}
invisible(data[,DEVICE:=DEVICE-2])
## 30 minutes
invisible(data[!is.na(NEOUTCOME1),outcome30minAnyVsNormal:=0])
invisible(data[!is.na(NEOUTCOME1) & NEOUTCOME1>=2,outcome30minAnyVsNormal:=1])

invisible(data[,outcome30minTreatmentVsNormal:=outcome30minAnyVsNormal])
invisible(data[!NEOUTCOME1 %in% c(1,2), outcome30minTreatmentVsNormal:=NA])

invisible(data[,outcome30minStillVsNormal:=outcome30minAnyVsNormal])
invisible(data[!NEOUTCOME1 %in% c(1,4),outcome30minStillVsNormal:=NA])

invisible(data[,outcome30minAdmittedVsNormal:=outcome30minAnyVsNormal])
invisible(data[!NEOUTCOME1 %in% c(1,6),outcome30minAdmittedVsNormal:=NA])

## 24 hours
invisible(data[!is.na(NEOUTCOME2),outcome24hAnyVsNormal:=0])
invisible(data[!is.na(NEOUTCOME2) & NEOUTCOME2>=2,outcome24hAnyVsNormal:=1])

invisible(data[,outcome24hTreatmentVsNormal:=outcome24hAnyVsNormal])
invisible(data[!NEOUTCOME2 %in% c(1,2), outcome24hTreatmentVsNormal:=NA])

invisible(data[,outcome24hDeathVsNormal:=outcome24hAnyVsNormal])
invisible(data[!NEOUTCOME2 %in% c(1,3),outcome24hDeathVsNormal:=NA])

invisible(data[,outcome24hDeathTreatVsNormal:=outcome24hAnyVsNormal])
invisible(data[!NEOUTCOME2 %in% c(1,2,3),outcome24hDeathTreatVsNormal:=NA])

## 5 minutes
invisible(data[!is.na(APGAR55),lowAPGAR5:=0])
invisible(data[APGAR55<7,lowAPGAR5:=1])
```

\newpage
# ANALYSES FOR SECONDARY OUTCOMES

## Secondary outcome low apgar score at 5th minute (<7)

```{r}
xtabs(~DEVICE+lowAPGAR5,data=data)
fit <- glm(lowAPGAR5~DEVICE,data=data,family=binomial())
summary(fit)
```

\newpage
## Secondary outcome stillbirths at 30 minutes

```{r}
xtabs(~DEVICE+outcome30minStillVsNormal,data=data)
fit <- glm(outcome30minStillVsNormal~DEVICE,data=data,family=binomial())
summary(fit)
```

\newpage
## Secondary outcome death at 24 hours

```{r}
xtabs(~DEVICE+outcome24hDeathVsNormal,data=data)
fit <- glm(outcome24hDeathVsNormal~DEVICE,data=data,family=binomial())
summary(fit)
```

\newpage
## Secondary outcome in treatment at 24 hours

```{r}
xtabs(~DEVICE+outcome24hTreatmentVsNormal,data=data)
fit <- glm(outcome24hTreatmentVsNormal~DEVICE,data=data,family=binomial())
summary(fit)
```

\newpage
## Secondary outcome death at 24 hours and/or in treatment at 24 minutes

```{r}
xtabs(~DEVICE+outcome24hDeathTreatVsNormal,data=data)
fit <- glm(outcome24hDeathTreatVsNormal~DEVICE,data=data,family=binomial())
summary(fit)
```

